Open source symbolic multibody dynamics software

### 2012-02-21 PetersonGedeHubbard2012.tex
Fixed A' to A definition

\begin{align}
    \prime{A} &\triangleq \tilde{M}^{-1} \tilde{A} \\
    \prime{B} &\triangleq \tilde{M}^{-1} \tilde{B}
\end{align}

Now we will have matrices $\prime{A}$ and $\prime{B}$ which are of size $(o +
n) \times (o - m + n - l)$ and $(o + n) \times p)$. We need to now extract only
the rows which are associated with the independent quantities. We will define
% Is there a better way to write transforming A' to A, B' to B?
% Could we use the permutation matrices here?
the reduced matrices as $A$ and $B$. We will also define the state space vector
$x = \left[\delta\bm{q}_i,\,\delta\bm{u}_i\right]^{T}$; we now have the
traditional state space representation.

%For stability analyses, one must examine the stability of the mapping $\delta
%\bm{q}_i \to \bm{\dot{q}}_i$.  This can be done by first solving for
%$\delta\bm{\dot{x}} = \left[\delta\bm{\dot{q}},\,\delta\bm{\dot{u}}\right]^{T}$, then selecting
%the independent rows of these equations ($n-l+o-m$ of them) to form a square
%matrix whose eigenvalues govern the stability of the system about the point of
%linearization.

>>>>

\begin{align}
    A\prime &\triangleq \tilde{M}^{-1} \tilde{A} \\
    B\prime &\triangleq \tilde{M}^{-1} \tilde{B}
\end{align}

Now we will have matrices $A\prime$ and $B\prime$ which are of size $(o +
n) \times (o - m + n - l)$ and $(o + n) \times p)$. We need to now extract only
the rows which are associated with the independent quantities. We will call the
new matrices reduced matrices $A$ and $B$ and compute them with the following

\begin{align}
    P \prime &\triangleq \begin{matrix}
        P_{qi} & \bm{O}_{(n - l) \times (o - m)} \\
        \bm{O}_{(o - m) \times (n - l)} & P_{ui}
    \end{matrix} \\
    A &\triangleq P\prime^T A\prime \\
    B &\triangleq P\prime^T B\prime \\
\end{align}

We will also define the state space vector $x =
\left[\delta\bm{q}_i,\,\delta\bm{u}_i\right]^{T}$; we now have the traditional
state space representation which only contains independent quantities.
